### 2017-10-12 manuscript.rmd
fixed var name
Added bootstraps and posteriors to species tree

	# Graphics
	library( cowplot )
	library( ggtree )
#	library( GGally )
	library( fields ) # tim.colors
	library( seriation )
	library( gridExtra )
#	library( RGraphics )
  library( factoextra )
  library( FactoMineR )

@@

	# Configure knitr, see http://yihui.name/knitr/options
	opts_knit$set( 
	  progress = TRUE, 
	  verbose = TRUE, 
	  include=FALSE, 
	  cache=TRUE
	 )

@@

@@

	species_tree = ape::read.tree( input_file_ml )
  bootstrap_trees = ape::read.tree( input_file_bootstraps )

@@

  phylobayes_trees = unlist( phylobayes_tree,recursive=FALSE )

@@

```{r pre_process_species_trees, include=FALSE, cache=TRUE}

@@

	species_tree = 
	  ape::root( 
	    species_tree, 
	    c( "Nematostella_vectensis", "Aiptasia_pallida" ), 
	    resolve.root=TRUE 
	   )

@@

	# Update species names
	species_tree$tip.label = sub( '_', ' ', species_tree$tip.label )

@@

@@

```{r summary_table, results='asis', cache=TRUE, echo=FALSE, comment=NA, warning=FALSE}

@@

```{r species_phylogram, cache=TRUE, echo=FALSE, comment=NA, warning=FALSE, fig.cap="Phylogram of siphonophore relationships. Node labels indicate bootstrap support percent, unnumbered nodes have 100% support. The image was rendered with ggtree [@Yu:2016fo]" }

@@

	p = ggtree( species_tree ) +
			geom_text( aes( label=support ), vjust=-.5, hjust=1, size=2.5, col="darkslategray4" ) +
			geom_tiplab( size=3 ) +
			xlim( NA, 4 ) +
			geom_cladelabel( node=cystonectae_node, label="Cystonectae", align=FALSE, offset=1, color='red' ) +
			geom_cladelabel( node=calycophora_node, label="Calycophora", align=FALSE, offset=1, color='blue' ) +
			geom_strip(
				which( species_tree$tip.label=="Agalma elegans" ),
				which( species_tree$tip.label=="Apolemia white" ),
				barsize=0.5,
				color='orange',
				offset=1,
				label='"Physonectae"'
			) +
			geom_strip(
				which( species_tree$tip.label=="Hydractinia symbiolongicarpus" ),
				which( species_tree$tip.label=="Nematostella vectensis" ),
				barsize=0.5,
				color='gray',
				offset=1,
				label='"Outgroups"'
			)

	flip( p, euphysonectae_node, calycophora_node )

>>>>

	# Graphics
	library( cowplot )
	library( ggtree )
	library( fields ) # tim.colors
	library( seriation )
	library( gridExtra )
  library( factoextra )
  library( FactoMineR )

@@

	# Configure knitr, see http://yihui.name/knitr/options
	opts_knit$set( 
	  progress=TRUE, 
	  verbose=TRUE, 
	  include=FALSE, 
	  cache=TRUE,
	  echo=FALSE,
	  message=FALSE
	 )

@@

```{r functions}

  get_node_support = function(  tree, treeset, threshold=100 ){
    # Returns a vector corresponding to nodes in tree, with percent of trees 
    # in treeset that contain the corresponding bipartition
    clades = prop.clades(tree, treeset) / length(treeset)
    nodes = c(rep(NA,length(tree$tip.label)), round(clades*100)) # Offset with NA values for tips
    nodes[ length(tree$tip.label) + 1 ] = NA # Set the root value to NA, not a robust way to find root but works in this case

    nodes[ nodes >= threshold  ] = NA

    return(nodes)
  }

  fix_names = function( tree ){
    # Apply changes to any tip names
    tree$tip.label = sub( '_', ' ', tree$tip.label )
    return( tree )
  }

@@

	species_tree = ape::read.tree( input_file_ml )
  species_tree = fix_names( species_tree )

  bootstrap_trees = ape::read.tree( input_file_bootstraps )

@@

  phylobayes_trees = unlist( phylobayes_trees,recursive=FALSE )
  class( phylobayes_trees  ) = "multiPhylo"

  bootstrap_trees = lapply( bootstrap_trees, fix_names )
  phylobayes_trees = lapply( phylobayes_trees, fix_names )

@@

```{r pre_process_species_trees}

@@

	species_tree = 
	  ape::root( 
	    species_tree, 
	    c( "Nematostella vectensis", "Aiptasia pallida" ), 
	    resolve.root=TRUE 
	   )

@@

@@

	# Update species names
	species_ultrametric$tip.label = sub( '_', ' ', species_ultrametric$tip.label )

@@

```{r summary_table, results='asis', echo=FALSE, comment=NA, warning=FALSE}

@@

```{r species_phylogram, echo=FALSE, comment=NA, warning=FALSE, fig.width=6.5, fig.height=7, fig.cap="Phylogram of siphonophore relationships. Node labels indicate bootstrap support percent, unnumbered nodes have 100% support. The image was rendered with ggtree [@Yu:2016fo]" }

@@

	p_phylogram = ggtree( species_tree ) +
			# geom_text( aes( label=support ), vjust=-.5, hjust=1, size=2.5, col="darkslategray4" ) +
	    geom_text(aes(label=get_node_support(species_tree, bootstrap_trees)), vjust=-.5, hjust=1, size=2.5, col="red") +
      geom_text(aes(label=get_node_support(species_tree, phylobayes_trees)), vjust=1.5, hjust=1, size=2.5, col="blue") +
			geom_tiplab( size=3 ) +
			xlim( NA, 4 ) +
			geom_cladelabel( node=cystonectae_node, label="Cystonectae", align=FALSE, offset=1, color='red' ) +
			geom_cladelabel( node=calycophora_node, label="Calycophora", align=FALSE, offset=1, color='blue' ) +
			geom_strip(
				which( species_tree$tip.label=="Agalma elegans" ),
				which( species_tree$tip.label=="Apolemia white" ),
				barsize=0.5,
				color='orange',
				offset=1,
				label='"Physonectae"'
			) +
			geom_strip(
				which( species_tree$tip.label=="Hydractinia symbiolongicarpus" ),
				which( species_tree$tip.label=="Nematostella vectensis" ),
				barsize=0.5,
				color='gray',
				offset=1,
				label='"Outgroups"'
			)

	flip( p_phylogram, euphysonectae_node, calycophora_node )
